---
title: "p8105_hw5_ag2965"
author: "Aakriti Shukla"
date: "2022-11-07"
output: github_document
editor_options: 
  chunk_output_type: inline
---

```{r, include = FALSE}
library(tidyverse)
library(pwr)
library(stringr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

#Problem 1

```{r, eval=FALSE}
con_01 = read_csv("data/con_01.csv")
con_02 = read_csv("data/con_02.csv")
con_03 = read_csv("data/con_03.csv") 
con_04 = read_csv("data/con_04.csv") 
con_05 = read_csv("data/con_05.csv") 
con_06 = read_csv("data/con_06.csv") 
con_07 = read_csv("data/con_07.csv")
con_08 = read_csv("data/con_08.csv")
con_09 = read_csv("data/con_09.csv")
con_10 = read_csv("data/con_10.csv")
exp_01 = read_csv("data/exp_01.csv")
exp_02 = read_csv("data/exp_02.csv")
exp_03 = read_csv("data/exp_03.csv")
exp_04 = read_csv("data/exp_04.csv")
exp_05 = read_csv("data/exp_05.csv")
exp_06 = read_csv("data/exp_06.csv")
exp_07 = read_csv("data/exp_07.csv")
exp_08 = read_csv("data/exp_08.csv")
exp_09 = read_csv("data/exp_09.csv")
exp_10 = read_csv("data/exp_10.csv")
```

#how to remove the data/ and the .csv?
```{r}
prob1_df2<-data.frame(first_column=c("con_01","con_02","con_03","con_04","con_05"))
```

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.



#Problem 2
Homicide data in 50 large U.S. cities - The Washington Post data

Let's load the data. 
```{r}
homicides_df <- read.csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"))%>%
  janitor::clean_names()

homicides_df_total=homicides_df%>%
  janitor::clean_names()%>%
  count()

homicides_df_state=homicides_df%>%
  janitor::clean_names()%>%
  group_by(state)%>%
  summarize

homicides_df_city=homicides_df%>%
  janitor::clean_names()%>%
  group_by(city)%>%
  summarize
```


There are 50 cities and 27 states in this dataset. There are 52,179 total homicides represented in this dataset.The variables included in this dataframe include the case ID, the date the homicide was reported, the victim’s first and last name, age, race, and sex, as well as the the following regarding the location of the crime: the city and state and the latitude and longitude. There is also data on the disposition of the case, which includes closed without arrest, closed by arrest, and opened/no arrest. The  dataset has `r nrow(homicides_df)` rows and `r ncol(homicides_df)` columns.

Below, we have created a table with the number of unsolved and total homicides by city. Unsolved homicides are those that have a disposition of "Closed by arrest" or "Open/No arrest".
```{r}
unsolved_homicides=homicides_df%>%
  janitor::clean_names()%>%
    unite(city_state, c(city, state), sep = ", ")%>%
    group_by(city_state)%>%
    summarize(
      unsolved=sum(disposition=="Closed by arrest" | disposition=="Open/No arrest"),
      total=n())

unsolved_homicides%>%
  knitr::kable()
```

We then created a dataframe for homicides in Baltimore and used the prop.test function to estimate the proportion of homicides that are unsolved. 

```{r}
baltimore_homicides=unsolved_homicides%>%
  filter(city_state %in% "Baltimore, MD")
```

```{r}
prop_unsolved=function(x_sum, n_total) {

proptest_unsolved=
  prop.test(
        x=x_sum,
        n=n_total,
        conf.level = 0.95, 
        alternative=c("two.sided"),
        correct = TRUE)%>%
  broom::tidy()%>%
   select(estimate,conf.low,conf.high)

proptest_unsolved
}

prop_unsolved(pull(baltimore_homicides,unsolved), pull(baltimore_homicides,total))
```

We then used this function to for each of the cities in the dataset and extracted the proportion of unsolved homicides and the confidence interval for each using the purrr::map2 function. We also creatd a plot that shows the estimates and CIs for each city along with error bars.
```{r}
unsolved_cities=unsolved_homicides%>%
  mutate(
    prop_unsolved_df = 
      map2(.x = unsolved, .y = total, ~prop_unsolved(x = .x, n = .y))
  ) %>% 
  unnest(prop_unsolved_df)

unsolved_cities
  
  ggplot(data=unsolved_cities, aes(x = fct_reorder(city_state, estimate), y = estimate)) +
geom_point() +
labs(x = "Location", y= "Proportion") +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.5) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    ggtitle("Proportion of Unsolved Homicides by Location")
```


#Problem 3

We created a simulation to explore power in a one-sample t-test with the following design elements: n=30, σ=5, μ=0 and we generated 5000 datasets from the mode. For each dataset, we have saved μ̂  and the p-value arising from a test of H:μ=0 using α=0.05.I have repeated this for μ={1,2,3,4,5,6}.

```{r}
t_test = function(df){
  power_df <- t.test(df,
         alternative = c("two.sided"),
         mu = 0,
         conf.level = 0.95) %>%
    broom::tidy()
  return(power_df)
}

generate_results = function(mu = 0,
                            sigma = 5,
                            n_iter = 50,
                            n_obs = 30){

new_list = list()

for (i in 1:n_iter) {
  temp_vec = rnorm(n = n_obs, mean = mu, sd = sigma)
  new_list[[i]] = temp_vec
}

stats_tib =
  tibble(
    data = new_list
  ) %>%
  mutate(
    ttest_results = map(.x = data, ~t_test(.x))
  ) %>%
  unnest(ttest_results) %>%
  janitor::clean_names() %>%
  select(estimate, p_value)


final_tib = stats_tib %>%
  mutate(
    rej = p_value < 0.05
  ) %>%
  summarize(
    tot = n(),
    tot_rej = sum(rej),
    prop_rej = tot_rej/tot,
    avg_mu_hat = mean(estimate)
  )
return(final_tib)
}

generate_results()

new_tib =
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)
  ) %>%
  mutate(
    results = map(.x = mu, ~generate_results(mu = .x))) %>%
      unnest(results)

rej_tib=new_tib%>%
  group_by(mu)%>%
  filter(p_value<0.05)%>%
  summarize(rej_estimate=mean(estimate))
```


Below, I have made a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. I have found that as effect size increases, as does power. 

```{r}
power_test=ggplot(data=new_tib, aes(x = mu, y = prop_rej)) +
geom_bar(stat="identity") +
labs(x = "Mu", y= "Proportion Rejected") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    ggtitle("Power of test")

power_test
```

Below, I have  made a plot (left panel) showing the average estimate of μ̂  on the y axis and the true value of μ on the x axis. 
```{r}
mu_hat_estimate=ggplot(data=new_tib, aes(x = mu, y = avg_mu_hat)) +
geom_bar(stat="identity") +
labs(x = "Mu", y= "Estimate of Mu-hat") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    ggtitle("Mu-hat at True Values of Mu")

mu_hat_estimate

```
Make a second plot (or overlay on the first) the average estimate of μ̂  only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂  across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

The sample average of mu-hat for across tests for which the null hypothesis is rejected is not approximately equal to the true value of mu because these samples were sufficiently different than mu, allowing for the rejection of the null hypothesis.

```{r}
t_test = function(df){
  power_df <- t.test(df,
         alternative = c("two.sided"),
         mu = 0,
         conf.level = 0.95) %>%
    broom::tidy()
  return(power_df)
}

generate_results = function(mu = 0,
                            sigma = 5,
                            n_iter = 50,
                            n_obs = 30){

new_list = list()



for (i in 1:n_iter) {
  temp_vec = rnorm(n = n_obs, mean = mu, sd = sigma)
  new_list[[i]] = temp_vec
}


stats_tib =
  tibble(
    data = new_list
  ) %>%
  mutate(
    ttest_results = map(.x = data, ~t_test(.x))
  ) %>%
  unnest(ttest_results) %>%
  janitor::clean_names() %>%
  select(estimate, p_value)

rej_tib = stats_tib %>%
  mutate(
    rej = p_value < 0.05
  ) %>%
  summarize(
    tot = n(),
    tot_rej = sum(rej),
    prop_rej = tot_rej/tot,
    rej_avg_mu_hat = mean(estimate))%>%
  
  
  group_by(mu)%>
  filter(p_value<0.05)%>%
  summarize(rej_avg_mu_hat=estimate)
return(rej_tib)
}

rej_tib%>%

  )

}

generate_results()

new_rej_tib =
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)
  ) %>%
  mutate(
    results = map(.x = mu, ~generate_results(mu = .x))) %>%
      unnest(results)


rej_mu_hat_estimate=ggplot(data=rej_tib, aes(x = mu, y = rej_avg_mu_hat)) +
geom_bar(stat="identity") +
labs(x = "Mu", y= "Estimate of Mu-hat for Rejected Samples") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    ggtitle("Mu-hat at True Values of Mu for Rejected Samples")


library(patchwork)
mu_hat_estimate

final_tib = stats_tib %>%
  mutate(
    rej = p_value < 0.05
  ) %>%
  summarize(
    tot = n(),
    tot_rej = sum(rej),
    prop_rej = tot_rej/tot,
    avg_mu_hat = mean(estimate)
  )
return(final_tib)
}

generate_results()

new_tib =
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)
  ) %>%
  mutate(
    results = map(.x = mu, ~generate_results(mu = .x))) %>%
      unnest(results)
  

mu_hat_estimate=ggplot(data=new_tib, aes(x = mu, y = avg_mu_hat)) +
geom_bar(stat="identity") +
labs(x = "Mu", y= "Estimate of Mu-hat") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    ggtitle("Mu-hat at True Values of Mu")

mu_hat_estimate

```
